---
headless: true
encoding: UTF-8
---

```{r knitrrrr, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  out.width = "100%"
)
```

```{r chart, include=FALSE}
updated <- format(Sys.time(), "%m-%d-%Y (at %H:%M)")
pub <-  readRDS(file.path(local.storage, sprintf("bibliography_%s.rds", "en")))
n <- nrow(pub)
```

# About

This website serves as an archive for scientific publications at 
University of Inland Norway (registered in Cristin since the institution was 
established on January 1, 2017). 
It is updated monthly.

The archive was last updated **`r updated`** and contains **`r n`** publications.

Use [the archive](#archive) to find publications for faculties and departments 
at the university for a specific year or month. You can also use the search 
function to find individual publications by using, for example, the author's 
name or title.

The estimation of the 17 Sustainable Development Goals (SDGs) outlined in 
Agenda 2030 is based on available abstracts from publications, and is calculated
using machine learning based on a large language model (LLM) and semantic analysis. 
The model will be made available pending peer-review.

You may also visit the 
[Zotero library](https://www.zotero.org/groups/5881554/inn_archive/library).